\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-06-18 paper/supporting_information.tex
updates to PCA figure

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components for correlation orders and reduction types.}  \textit{Order} refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph:272;
    word: 300; rest: 400). \textbf{a.~Cumlative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw acitivity patterns (Order 0). \textbf{b.-e.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.:
    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. }
\label{fig:pca}
\end{figure}

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components for correlation orders and reduction types.}  \textit{Order} refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400). \textbf{a.~Cumlative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw acitivity patterns (Order
  0). \textbf{b.~Proportion of components to explain 85\% variance for
    each condition and order.} PCA was performed for dynamic
  correlations for each order.  Proportion was calculated by finding
  the number of components to explain 85\% variance and dividing by
  the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400).  Dynamic correlation were calculated for
    orders 1-4 using PCA (solid lines) and eignenvector centrality
    (dashed lines) to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.  \textbf{c.-f.~Cumlative percent
    variance as a function of proportion of components for Orders 1.-4.:
    PCA.} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{g.-j.~Cumlative percent
    variance as a function of proportion of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. }
\label{fig:pca}
\end{figure}
